---
title: "Big Mac"
output: html_notebook
---

This dataset has been uploaded on Kaggle website. 

```{r}
#dollars_ex is the conversation rate with the local currency. 

#import data
library(dplyr)

bigmac <- read.csv("BigmacPrice.csv", header = TRUE)

#rename columns
names(bigmac)[names(bigmac) == "name"] <- "country"

print(BigMac)

#average price per country
library(dplyr)

bigmac_grouped <- bigmac %>%
  group_by(country)

bigmac_avg <- bigmac_grouped %>%
  summarise(avg_price = mean(dollar_price))

print(bigmac_avg)

#graph avg
library(ggplot2)

graph_bigmac_avg <- ggplot(bigmac_avg, aes(x=country, y=avg_price)) +
  geom_segment( aes(x=country, xend=country, y=0, yend=avg_price
), color="skyblue") +
  geom_point( color="blue", size=4, alpha=0.6) +
  labs(
  title = "Average price of a bigmac per country since 2000",
  y = "Average price in dollars", x = "Countries"
)+
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank() 
)

graph_bigmac_avg
```

On the blue graph, we see that Norway has the most expensive bigmac in average, and Oman and Kowait the most cheepest ones. 
For the analysis, we select the few following countries: Norway, Oman, Mexico, Germany and Thailand. 
```{r}
#filter countries
library(ggplot2)
library(dplyr)

bigmac_subset <- bigmac %>% 
  filter(country %in% c("Norway", "Oman", "Thailand", "Mexico", "France"))

bigmac_subset$date <- as.Date(paste0(bigmac_subset$date, "-01-01"))

ggplot(data = bigmac_subset, aes(x = date, y = dollar_price, color = country)) +
  geom_line() +
  labs(title = "BigMac prices through years",
       x = "date",
       y = "dollar_price") +
  scale_color_discrete(name = "country")

#Compute the number of data per country
library(dplyr)

data_country <- bigmac %>% 
  group_by(country) %>% 
  summarise(num_data = n())
  
print(data_country)
```
We see that Oman has only 9 data and Germany only 23. It is a few compared to Norway that has 33 data and Mexico 37. 

